\documentclass[overlapped, line, 10pt]{res}
%\documentclass[letterpaper, centered, 10pt]{res}

\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\addtolength{\textheight}{1 cm} \addtolength{\voffset}{-0.5 cm}

\begin{document}

\renewcommand{\namefont}{\Large\textbf}

\name{Oleg Kamaev}

\begin{resume}

\hspace*{-\sectionwidth}E-mail:  oleg.v.kamaev@gmail.com \hfill Ontario, Canada\\
\hspace*{-\sectionwidth}Phone: (613) 985-9496\\
\hspace*{-\sectionwidth}\url{https://github.com/olegkamaev}

%---------------------------------------------------------------------------
\section{\sc Summary of Qualifications}
\setlength{\leftmargini}{1 em}
\begin{itemize}
\item Over 5 years of experience in quantitative data analysis, mathematical modeling of physical processes, numerical programming.
\item Solid academic background in Physics, Applied Mathematics, Statistical Analysis.
\item Author and co-author of over 20 publications in peer-reviewed journals and proceedings of national and international conferences. 
\item A quick learner who can communicate clearly and effectively. 
\item Highly energetic and result-oriented with strong analytical and problem-solving skills.
\end{itemize}
\textbf{Areas of Expertise:}\\
\begin{tabular}{p{5cm} p{5cm} p{5cm}}
- data mining & - statistical inference  & - algorithms design \\
- machine learning & - relational databases & - software development \\
- predictive analytics & - Monte Carlo simulations & - technical writing
\end{tabular}

\textbf{Technical Skills:}
\begin{itemize}
\item Programming languages: MATLAB, Python, Fortran
\item Relational databases: MySQL, MS Access
\item Version control systems: CVS, Git
\item UNIX environments: Linux, Mac OS
\item Statistical techniques: regression, MLE, nonlinear optimization, pattern search, principal component analysis, neural networks
\item Application software: MS Excel, VBA macros, MS PowerPoint, Origin, LaTeX, Emacs, HTML
\end{itemize}

\section{\sc Experience}
\begin{format}
\title{l} \dates{r} \\
\body
\end{format}

\title{Research Fellow / Lecturer}
\dates{2011 -- 2014}
\begin{position}
Queen's University, Kingston, Canada
\begin{itemize}
\item[--] Processed, cleaned, and analyzed (MATLAB, Python) large datasets collected by a world-leading experiment to search for dark matter and other rare events. 
\item[--] Fitted physical models to experimental data for event classification; applied regression and unconstrained nonlinear optimization. Utilized maximum likelihood analysis to test signal hypothesis against background model.
\item[--] Effectively communicated results at leading national/international conferences (see, e.g., a talk that I gave at 2013 Canadian Association of Physicists Congress: \url{http://tinyurl.com/oov4ha4}).
\item[--]Mentored several M.Sc.~and undergraduate research students on data analysis including MATLAB programming and statistical techniques.
\end{itemize}
\end{position}

\title{Research Associate}
\dates{2008 -- 2010}
\begin{position}
University of Minnesota, Minneapolis, USA\\
Cryogenic Dark Matter Search experiment:
\begin{itemize}
\item[--] Investigated neural network discrimination technique for signal/background separation. Used advanced statistical methods to perform high-dimensional data analysis.
\item[--] Developed software to optimize and automate techniques for setting event selection criteria that increased the expected signal sensitivity while minimizing backgrounds; applied constrained minimization using pattern search in MATLAB for numerical optimization.
\end{itemize}

\newpage
\opening

\vspace{1ex}
\begin{itemize}
\item[--] Led the work to establish statistical criteria to identify and remove bad datasets due to periods of poor detector performance.
\item[--] Designed and programmed data analysis tools (MATLAB, MySQL, Excel) to estimate concentration of radioactive contaminations in samples; being used since 2010 to routinely analyze materials. Developed Monte Carlo simulations of the corresponding physical processes. 
\item[--] Prepared results and published analysis papers in refereed scientific journals.
\end{itemize}
\end{position}

\title{Research Assistant}
\dates{2004 -- 2007}
\begin{position}
Illinois Institute of Technology, Chicago, USA\\
Particle physics experiments at Fermilab:
\begin{itemize}
\item[--] Developed specialized algorithms (Fortran, C\texttt{++}) to reconstruct, observe, and measure properties of rare events from $\sim$TB datasets. Published results.
\item[--] Applied unbinned generalized likelihood fits to extract model parameters from low-statistics samples. Used Monte Carlo technique to estimate systematic errors and confidence intervals.
\item[--] Authored a computer program to readout low voltages (hundreds of channels) from the various crate power supplies and write them into SQL database.
\end{itemize}
\end{position}

\section{\sc Education, Certifications}
\textbf{Ph.D. in Physics \hfill 2007}\\
Illinois Institute of Technology, Chicago, USA

Certificates in SQL, Relational Design Theory, UML\\
Stanford online

\section{\sc Selected Refereed Publications}

\begin{itemize}
    \item R.~Agnese {\it et al.}  [SuperCDMS Collaboration],
    ``Search for Low-Mass Weakly Interacting Massive Particles Using Voltage-Assisted Calorimetric Ionization Detection in the SuperCDMS Experiment,'' Phys.\ Rev.\ Lett.\  {\bf 112}, 041302 (2014).
    \item R.~Agnese {\it et al.}  [CDMS Collaboration],
  ``Silicon Detector Dark Matter Results from the Final Exposure of CDMS II,''
  Phys.\ Rev.\ Lett.\ {\bf 111}, 251301 (2013).
    \item Z.~Ahmed {\it et al.}  [CDMS collaboration],
    ``Dark Matter Search Results from the CDMS II Experiment,''
    Science {\bf 327}, 1619 (2010).
    \item O.~Kamaev \textit{et al.} [HyperCP Collaboration],
     ``Study of the Rare Hyperon Decay ${\boldmath
       \Omega^\mp \to \Xi^\mp \: \pi^+\pi^-}$,'' Phys.\ Lett.\ B. \textbf{693}, 236 (2010).
%     \item I.~Eremin, O.~Kamaev, and M.~V.~Eremin,
%     ``Possible isotope effect on the resonance peak formation in high-$T_{c}$ cuprates,''
%     Phys. Rev. B \textbf{69}, 094517 (2004).

\end{itemize}

\section{\sc Additional Information}
Permanent Resident of Canada.

\end{resume}

\end{document}
